---
title: "Introduction to fun r packages"
author: "Shiyuan Xu, Ying Hong"
date: "2022-11-12"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fun)
library(fortunes)
library(cowsay)
```
# Part 1-- Introductions of R Packages

## Interesting Package 1-- "cowsay"

`Cowsay` prints out messages and shapes of animals. Names of animals are displayed below:
```{r}
names(animals)
```
There are 44 animal names in "cowsay".

### Function `say()`: 
prints out messages that are spoken by animals.

### Arguments in function `say()`:
- `what`: a string, a message that you want the animal to say. A special case: `what="time"` can output the current time.
- `by`: a string, an animal character name (from the 44 animal names). Use `by = "random"` to select a random character.
- `type`: specifies the type of message that the animal say, can be either "message" (default), "warning", or "string".
- `by_color`: specifies the color(s) for the animal.

### Example 1-- An anxious cat is telling us what current time is
```{r}
say(what = "time", 
    by = "anxiouscat")
```
### Example 2-- Christmas greetings from a snowman in rainbow color
```{r}
say("Merry Christmas!", 
    by = "snowman", 
    what_color = rgb(.1, .2, .3),
    by_color = "rainbow")
```
### Example 3-- A warning message
```{r}
say(what = "Wake up and study for your finals!", 
    by = "pig", 
    type = "warning")
```


## Interesting Package 2-- "fortunes":

### Arguments in function `fortune()`:
- `which`: an integer, row number of `fortunes` dataframe in `fortunes` library.
- `author`: a string, a author name in `fortunes` library.

### Example 1-- Function `fortune()` randomly prints a fortune message from `fortunes` dataframe by default.
```{r}
fortune()
```

### Example 2-- A fortune message from a specific row
```{r}
fortune(which = 10)
```
By specifying `which = 10`, we obtain a quote in the 10th row from `fortunes` dataframe.

### Example 3-- A fortune message from a specific author

First, let's take a look at the first 6 rows in the `fortunes` dataframe.
```{r}
df_fortunes <- read.fortunes()
head(df_fortunes)
```
The columns in the dataframe are: quote, author, context, source, and date.
```{r}
num_rows <- nrow(df_fortunes)
num_rows
```
There are `r num_rows` rows in the `fortunes` dataframe.

From the `fortunes` dataframe, we can see all the author names. Below is the first 6 rows in the column `author`.
```{r}
head(df_fortunes["author"])
```
By specifying `author = "Robert Gentleman"`, we can extract an random quote from Robert Gentleman from the `fortunes` dataframe, along with its souce and date.
```{r}
fortune(author = "Robert Gentleman")
```

# Part 2-- Combination of "Cowsay" and "Fortunes" Packages

This is an interactive R Markdown document using Shiny. Readers may interact with the document by specifying the following inputs and see the results immediately.

- `animal`: you may choose any of the 44 animal characters from the above list
- `name`: your name
- `quote`: type "yes" if you want a fortune quote or "no" if you do not want a quote
- `number`: number of quotes
```{r eruptions, echo=TRUE}

inputPanel(
  textInput("animal", "animal", "pig"),
  textInput("name", "name", "name"),
  textInput("quote", "quote", "yes/no"),
  textInput("number", "number", "1")
)

renderPrint({
  if(input$quote == 'yes'){
  say(what = paste('hello,', input$name, ', it appears that you would like to hear a quote, here it is:'), by = input$animal)
  
  for (x in 1:input$number) {
  quote <- fortune()
  quote_to_string <- paste(quote,collapse = ' ')
  say(what = quote_to_string, by = input$animal)
  } 
    
  } else{
  say(what = paste('it appears that you do not wish to hear a quote'), by = input$animal)
  }
})

```

# Part 3-- References
https://cran.r-project.org/web/packages/cowsay/vignettes/cowsay_tutorial.html
https://www.rdocumentation.org/packages/fortunes/versions/1.5-4/topics/fortunes




